\section{Introduction}
\label{sec:intro}

Online social platforms are a privileged lens on how communities form, organise and exchange information. Bluesky, has rapidly grown as an alternative to X/Twitter and has attracted, in particular, a large and active scientific community of researchers, science journalists and outreach organisations. This makes it a compelling case study: a self-selected population whose online ties plausibly reflect real scholarly and communicative relationships.

This project collects, characterises and analyses the follow network of the scientific community on Bluesky. Starting from five thematic seed accounts, a snowball crawl over the platform's public endpoints yields a connected network of 15{,}000 accounts and about 1.67M follow relationships, enriched with node attributes (profile metadata) and a sample of posts. Three guiding questions are then posed: what is the structure of this network and does it differ from classical random models? Is it modular, and do its communities correspond to recognisable scientific domains? And how do information and behaviours spread over it?

The report is organised along the parts of the assignment. Section~\ref{sec:data} describes the data collection and the resulting network; Section~\ref{sec:analysis} characterises its topology and contrasts it with Erd\H{o}s--R\'enyi and Barab\'asi--Albert baselines; Section~\ref{sec:cd} detects and interprets its community structure; Section~\ref{sec:part3} addresses link prediction and diffusion (including a game-theoretic cascade); and Section~\ref{sec:open} tackles the open question of topical echo chambers. Across these analyses a consistent picture emerges: a dense, small-world, scale-free network with a strong community structure aligned with academic disciplines, and permeable rather than isolated topical chambers, which are drawn together in the final discussion.
